Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-10 cmsb22.tex
Paper updated w/ latest results

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Column "\(n\)" denotes the numbers of nodes of each model. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes. A number in bold indicates a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem & 9 & 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 & 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 & 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 & 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 & 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 & 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 & 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 & 18 & 0.04 & 0.08\\
    irons\_yeast & 18 & 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 & 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 & 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 & 6 & 0.03 & 0.03\\
    multivalued & 13 & 4 & 0.02 & 0.02\\
    n12c5 & 11 & 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 & 2 & 0.02 & 0.03\\
    n3s1c1b & 2 & 2 & 0.02 & 0.03\\
    n5s3 & 4 & 3 & 0.03 & 0.03\\
    n6s1c2 & 5 & 3 & 0.03 & 0.04\\
    n7s3 & 6 & 3 & 0.02 & 0.02\\
    raf & 3 & 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 & 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 & 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 & 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 & 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 & 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 & 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 & 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 & 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Column "\(n\)" denotes the numbers of nodes of each model. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    CASCADE3 & 183 & 1 & 82.86 & 12.83\\
    KYNURENINE-PATHWAY & 150 & 1000+ & 74.71 & 4.22\\
    SN5 & 2746 & ??? & DNF & DNF\\
    ERBB-RECEPTOR-SIGNALING & 247 & 1000+ & DNF & 9.27\\
    Executable\_file\_for\_cholocystokinin\_model & 383 & 1000+ & 1.55 & 3.57\\
    korkut\_2015a & 99 & 1000+ & DNF & 3.06\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 & 1000+ & 0.43 & 0.66\\
    Corral\_ThIL17diff\_15jan2021 & 92 & 1000+ & DNF & 0.91\\
    HIV-1 & 138 & 1000+ & DNF & 3.25\\
    Executable\_file\_for\_CaSQ\_derived\_mast\_cell\_activation\_model & 73 & 1000+ & 0.49 & 0.56\\
    Colitis\_associated\_colon\_cancer & 70 & 10 & 0.15 & 0.22\\
    INTERFERON-1 & 121 & 1000+ & 7.69 & 1.05\\
    TLGLSurvival & 61 & 318 & 0.59 & 0.48\\
    cho\_2016\_all\_pos & 200 & 1000+ & DNF & 3.00\\
    turei\_2016 & 4691 & ??? & DNF & DNF\\
    Human\_network & 1953 & 1000+ & DNF & DNF\\
    Executable\_file\_for\_CaSQ\_derived\_MAPK\_model & 181 & 1000+ & 75.32 & 2.26\\
    TCR-TLR5-SIGNALING-2018 & 130 & 48 & 0.93 & 0.53\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 & 1000+ & 36.21 & 2.27\\
    IMMUNE-SYSTEM & 164 & 1000+ & DNF & 2.78\\
    HMOX1-PATHWAY & 145 & 1000+ & 3.89 & 0.95\\
    Signaling\_in\_Macrophage\_Activation & 321 & 1000+ & 11.51 & 3.27\\
    FIBROBLASTS & 139 & 1000+ & DNF & 1.91\\
    S1\_Table & 1659 & 1000+ & DNF & DNF\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 & 78 & 40.59 & 2.15\\
    SIGNALING-IN-PROSTATE-CANCER & 133 & 1000+ & DNF & 1.70\\
    InflammatoryBowelDisease & 47 & 1 & DNF & 118.78\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 & 1000+ & 47.69 & 0.87\\
    IL\_6\_Signalling & 86 & 1000+ & 1.10 & 0.46\\
    VIRUS-REPLICATION-CYCLE & 154 & 1000+ & DNF & 1.16\\
    Executable\_file\_for\_Alzheimer\_model & 762 & 1000+ & DNF & 6.15\\
    ER-STRESS & 182 & 1000+ & 16.15 & 0.93\\
    RA\_apoptosis\_executable\_module & 180 & 1000+ & DNF & 0.96\\
    \bottomrule
  \end{tabular}
\end{table}

\vangiang{Regarding the time differences, the reason might be that my implementation uses an ASP encoding based on choice rules instead of disjunctive rules or constraint rules.}
\sylvain{Maybe\dots I don't know ASP well enough to be sure. The fact that you go through a predicate \texttt{p} which adds one level of indirection might also have some effect, I'm not sure.}
\vangiang{Oh. I think that this may be a reason. However, I think we should still use a predicate \texttt{p(v, x)} in the paper because of the readability.}

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Column \(n\) denotes the numbers of nodes of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    ``DNF'' means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes. A number in bold indicates a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem & 9 & 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate & 28 & 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma & 23 & 32 & 0.04 & 0.11\\
    davidich\_yeast & 10 & 12 & 0.03 & 0.08\\
    dinwoodie\_life & 15 & 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal & 13 & 1 & 0.04 & 0.05\\
    faure\_cellcycle & 10 & 2 & 0.04 & 0.04\\
    grieco\_mapk & 53 & 18 & 0.04 & 0.08\\
    irons\_yeast & 18 & 1 & 0.05 & 0.04\\
    jaoude\_thdiff & 103 & 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr & 40 & 8 & 0.06 & 0.04\\
    krumsiek\_myeloid & 11 & 6 & 0.03 & 0.03\\
    multivalued & 13 & 4 & 0.02 & 0.02\\
    n12c5 & 11 & 5 & \textbf{34.37} & 0.06\\
    n3s1c1a & 2 & 2 & 0.02 & 0.03\\
    n3s1c1b & 2 & 2 & 0.02 & 0.03\\
    n5s3 & 4 & 3 & 0.03 & 0.03\\
    n6s1c2 & 5 & 3 & 0.03 & 0.04\\
    n7s3 & 6 & 3 & 0.02 & 0.02\\
    raf & 3 & 2 & 0.03 & 0.02\\
    randomnet\_n15k3 & 15 & 3 & 0.04 & 0.05\\
    randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis & 34 & 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell & 13 & 1 & 0.02 & 0.03\\
    selvaggio\_emt & 56 & 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis & 12 & 3 & 0.05 & 0.06\\
    xiao\_wnt5a & 7 & 4 & 0.06 & 0.03\\
    zhang\_tlgl & 60 & 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 & 60 & 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns \(n\) and \(s\) denote the numbers of nodes (resp.\ input nodes) of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    ``DNF'' means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & \(n\) & \(s\) & \(|M|\) & PyBoolNet (s) & Trappist (s) \\
    \midrule
    InflammatoryBowelDisease & 47 & 0 & 1 & DNF & 21.90\\
    TLGLSurvival & 61 & 7 & 318 & 0.73 & 0.14\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 & 13 & 1000+ & 0.59 & 0.13\\
    Colitis\_associated\_colon\_cancer & 70 & 1 & 10 & 0.16 & 0.08\\
    mast\_cell\_activation\_model\_BCC & 73 & 19 & 1000+ & 0.64 & 0.15\\
    IL\_6\_Signalling & 86 & 15 & 1000+ & 3.30 & 0.10\\
    Corral\_ThIL17diff\_15jan2021 & 92 & 16 & 1000+ & DNF & 0.38\\
    korkut\_2015a & 99 & 12 & 1000+ & DNF & 0.61\\
    INTERFERON-1 & 121 & 55 & 1000+ & 8.36 & 0.19\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 & 4 & 78 & 40.81 & 0.33\\
    TCR-TLR5-SIGNALING-2018 & 130 & 5 & 48 & 0.88 & 0.12\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 & 11 & 1000+ & 63.62 & 0.21\\
    SIGNALING-IN-PROSTATE-CANCER & 133 & 11 & 1000+ & DNF & 0.32\\
    HIV-1 & 138 & 14 & 1000+ & DNF & 0.87\\
    FIBROBLASTS & 139 & 9 & 1000+ & DNF & 0.56\\
    HMOX1-PATHWAY & 145 & 56 & 1000+ & 5.16 & 0.18\\
    Kynurenine\_Pathway\_stable & 150 & 72 & 1000+ & DNF & 0.74\\
    VIRUS-REPLICATION-CYCLE & 154 & 25 & 1000+ & DNF & 0.19\\
    IMMUNE-SYSTEM & 164 & 13 & 1000+ & DNF & 0.67\\
    RA\_apoptosis\_executable\_module\_BCC & 180 & 59 & 1000+ & DNF & 0.16\\
    MAPK\_model\_BCC & 181 & 37 & 1000+ & 68.62 & 0.64\\
    ER-STRESS & 182 & 75 & 1000+ & 28.65 & 0.21\\
    CASCADE3 & 183 & 1 & 0 & 92.75 &  0.65\\
    cho\_2016\_all\_pos & 200 & 13 & 1000+ & DNF & 1.01\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 & 14 & 1000+ & 37.40 & 0.35\\
    ERBB-RECEPTOR-SIGNALING & 247 & 22 & 1000+ & DNF & 1.07\\
    Signaling\_in\_Macrophage\_Activation & 321 & 19 & 1000+ & 15.82 & 0.63\\
    cholocystokinin\_model\_BCC & 383 & 74 & 1000+ & 1.22 & 0.73\\
    Alzheimer\_model\_BCC & 762 & 237 & 1000+ & DNF & 1.03\\
    S1\_Table & 1659 & 521 & 1000+ & DNF & 44.85\\
    Human\_network & 1953 & 669 & 1000+ & DNF & 42.97\\
    SN5 & 2746 & 829 & ??? & DNF & DNF\\
    turei\_2016 & 4691 & 1257 & ??? & DNF & DNF\\
    \bottomrule
  \end{tabular}
\end{table}

% s obtained by: grep -c '^\([a-zA-Z0-9_-]*\),\s*\1\s*\(#.*\)\?$' models/*.bnet

\vangiang{Oh. I think that this may be a reason. However, I think we should still use a predicate \texttt{p(v, x)} in the paper because of the readability.}
\sylvain{To be honest, I don't think it is more readable\dots}
